---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bookprep

<!-- badges: start -->
![GitHub R package version](https://img.shields.io/github/r-package/v/marionlouveaux/bookprep?style=plastic)
![GitHub](https://img.shields.io/github/license/marionlouveaux/bookprep?style=plastic)
<!-- badges: end -->


<!-- Short description -->
The goal of {bookprep} is to prepare a {bookdown} project from a customizable bookdown skeleton and, if needed, a template for the chapters. {bookprep} helps creating reproducible yet flexible bookdown projects, for instance to deliver data analyses to customers following a standardized format.

## Installation

<!--

You can install the released version of bookprep from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("bookprep")
```
-->
 
You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("marionlouveaux/bookprep")
```

## Example
<!-- Brief demo usage -->

```{r example}
#library(bookprep)

```


## See also
<!-- Related packages -->
{bookdown}: https://bookdown.org/


## How to cite     


