---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bookprep

<!-- badges: start -->
![GitHub release (latest by date)](https://img.shields.io/github/v/release/marionlouveaux/bookprep?style=plastic)
![GitHub](https://img.shields.io/github/license/marionlouveaux/bookprep?style=plastic)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4806181.svg)](https://doi.org/10.5281/zenodo.4806181)
[![R build status](https://github.com/marionlouveaux/bookprep/workflows/R-CMD-check/badge.svg)](https://github.com/marionlouveaux/bookprep/actions)
[![Codecov test coverage](https://codecov.io/gh/marionlouveaux/bookprep/branch/master/graph/badge.svg)](https://codecov.io/gh/marionlouveaux/bookprep?branch=master)
<!-- badges: end -->


<!-- Short description -->
The goal of {bookprep} is to prepare a {bookdown} project from a customizable bookdown skeleton and, if needed, a template for the chapters. {bookprep} helps creating reproducible yet flexible bookdown projects, for instance to deliver data analyses to customers following a standardized format.

## Installation

<!--

You can install the released version of bookprep from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("bookprep")
```
-->
 
You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("marionlouveaux/bookprep")
```

## Example
<!-- Brief demo usage -->

```{r example}
library(bookprep)

# Create temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)
# browseURL(dir_tmp)

prepare_book(
  path = dir_tmp,
  template = system.file("book_template_example", package = "bookprep"),
  replacements = c(
    # replacements mandatory for the bookdown skeleton
    "book_title" = "My book",
    "author_name" = "Marion Louveaux",
    "creation_date" = "`r Sys.Date()`",
    "short_description" = "An example of book with {bookprep}.",
    # replacement specific to my template that you can add if you want
    "index_title" = "Context"
  )
)
```


## See also
<!-- Related packages -->
{bookdown}: https://bookdown.org/


## How to cite     

Please cite as:      
Marion Louveaux. (2021, May 26). bookprep: an R package to reproducibly prepare a {bookdown} project from a customizable skeleton and a template (Version v1.0.0). Zenodo. http://doi.org/10.5281/zenodo.4806181

## Code of Conduct

Please note that the bookprep project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


