---
editor_options: 
  chunk_output_type: console
---

```{r development}
pkgload::load_all()
library(testthat)
library(stringr)
library(purrr)
library(usethis)
```


```{r development, eval=FALSE}
# Add license
use_gpl3_license(name = "Marion Louveaux")

# Create inst directory and copy bookdown template in inst
dir_book <- "inst/skeleton"

if (!dir.exists(paths = here::here(dir_book))) {
  dir.create(path = here::here(dir_book), recursive = TRUE)
}
bookdown:::bookdown_skeleton(here::here(dir_book))

# Hide dev folder from build
usethis::use_build_ignore("dev/")

# git
usethis::use_git()

# description
usethis::use_description(
  fields = list(
    Title = "Prepares a bookdown project from a skeleton and a template",
    `Authors@R` = 'person("Marion", "Louveaux", email = "marion.louveaux@gmail.com",
                          role = c("aut", "cre"),
                          comment = c(ORCID = "0000-0002-1794-3748"))',
    Description = 'Prepares a bookdown project from a customizable bookdown skeleton and, if needed, a template for the chapters. Helps creating reproducible yet flexible bookdown projects, for instance to deliver data analyses to customers following a standardized format.',
    License = "GPL-3",
    URL = "https://github.com/marionlouveaux/bookprep",
    BugReports = "https://github.com/marionlouveaux/bookprep/issues"
  )
)

# Amend description import and suggests
attachment::att_amend_desc()
```


# Manual cleaning of bookdown skeleton

Keeping only the following files: "_bookdown.yml", "_output.yml", "index.Rmd", "preamble.tex", "README.md", "style.css". storing them in `/book_skeleton`.     

Cleaning info specific to bookdown package and replacing them by generic variable names:    
- Index.Rmd: create variable book_title, author_name, creation_date (default to `r Sys.Date()`), short_description, index_title and index_content   
- _bookdown.yml: reuse book_title variable  
- _output.yml: reuse book_title variable, add info that this book was published with {bookprep}             
- README.md: reuse variable book_title and specifies that this book was published with {bookprep}             



# Find and replace all variables in one text file of the book skeleton
```{r function-1}
#' Find and replace all variables in one of the files of the book skeleton
#'
#' @param file path of a file from skeleton: _bookdown.yml, _output.yml, index.Rmd, README.md
#' @param replacements a vector of correspondences between an input and an output. Input is fixed and corresponds to: book_title, author_name, creation_date, short_description and index_title
#' @importFrom stringr str_replace_all
#'
#' @return path of the modified file
#' @export
#'
#' @examples
find_and_replace <- function(file, replacements = c(
                               "book_title" = "My book",
                               "author_name" = "Marion Louveaux",
                               "creation_date" = "`r Sys.Date()`",
                               "short_description" = "An example of book with {bookprep}.",
                               "index_title" = "Context"
                             )) {
  file <- normalizePath(file, mustWork = FALSE)
  if (!file.exists(file)) {
    stop("The specified file does not exist.")
  }

  original_text <- readLines(con = file)
  modified_text <- str_replace_all(
    string = original_text,
    replacements
  )

  writeLines(enc2utf8(modified_text), con = file)
  file
}
```

```{r examples-1}
# copy to a temporary file to avoid overwriting the package
index_tmp <- tempfile(pattern = "index-")

file.copy(from = system.file("book_skeleton/index.Rmd", package = "bookprep"), to = index_tmp)

find_and_replace(
  file = index_tmp,
  replacements = c(
    "book_title" = "My book",
    "author_name" = "Marion Louveaux",
    "creation_date" = "`r Sys.Date()`",
    "short_description" = "An example of book with {bookprep}.",
    "index_title" = "Context"
  )
)
```

```{r test-1}
# copy to a temporary file to avoid overwriting the package
index_tmp <- tempfile(pattern = "index-")

file.copy(from = system.file("book_skeleton/index.Rmd", package = "bookprep"), to = index_tmp)

index_modified <- find_and_replace(
  file = index_tmp,
  replacements = c(
    "book_title" = "My book",
    "author_name" = "Marion Louveaux",
    "creation_date" = "`r Sys.Date()`",
    "short_description" = "An example of book with {bookprep}.",
    "index_title" = "Context"
  )
)

index_lines <- readLines(index_modified)
test_that("find_and_replace works", {
  expect_equal(index_lines[2], 'title: \"My book\"')
  expect_equal(index_lines[3], 'author: "Marion Louveaux"')
})
```


# Modify all variables in all files
```{r function-2}
#' Modify all variables in files from the book skeleton 
#'
#' @param path path to directory (skeleton) containing all files to modify
#' @param pattern regex to identify files to prepare (by default, all Rmd, yml and md files)
#' @inheritParams find_and_replace
#' @importFrom purrr map
#'
#' @return path from each modified file
#' @export
#'
#' @examples

prepare_files <- function(path, replacements = c(
                            "book_title" = "My book",
                            "author_name" = "Marion Louveaux",
                            "creation_date" = "`r Sys.Date()`",
                            "short_description" = "An example of book with {bookprep}.",
                            "index_title" = "Context"
                          ),
                          pattern = "[.]Rmd$|[.]yml$|[.]md$") {
  all_files_in_path <- list.files(path, full.names = TRUE)
  files_to_modify <- grep(
    pattern = pattern,
    all_files_in_path
  )
  map(
    all_files_in_path[files_to_modify],
    ~ find_and_replace(file = .x, replacements = replacements)
  )
  all_files_in_path[files_to_modify]
}
```


```{r examples-2}
# Create temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)
# browseURL(dir_tmp)

# prepare_files() requires a directory with some files inside to look for replacements
file.copy(from = system.file("book_skeleton", package = "bookprep"), to = dir_tmp, recursive = TRUE)

prepare_files(
  path = file.path("C:/Users/Marion/Desktop", "skeleton"),
  replacements = c(
    "book_title" = "My book",
    "author_name" = "Marion Louveaux",
    "creation_date" = "`r Sys.Date()`",
    "short_description" = "An example of book with {bookprep}.",
    "index_title" = "Context"
  )
)
```


```{r test-2}
# Create temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)
# browseURL(dir_tmp)

# prepare_files() requires a directory with some files inside to look for replacements
file.copy(from = system.file("book_skeleton", package = "bookprep"), to = dir_tmp, recursive = TRUE)

modified_files <- prepare_files(
  path = file.path(dir_tmp, "book_skeleton"),
  replacements = c(
    "book_title" = "My book",
    "author_name" = "Marion Louveaux",
    "creation_date" = "`r Sys.Date()`",
    "short_description" = "An example of book with {bookprep}.",
    "index_title" = "Context"
  )
)


test_that("prepare_files works", {
  # index modified
  index_lines <- modified_files[grep(pattern = "index[.]Rmd", x = modified_files)]
  index_content <- readLines(index_lines)
  expect_equal(index_content[3], 'author: "Marion Louveaux"')

  # _output.yml modified
  output_lines <- modified_files[grep(pattern = "_output[.]yml", x = modified_files)]
  output_content <- readLines(output_lines)
  expect_equal(output_content[6], '        <li><a href=\"./\">My book</a></li>')
})
```



# Prepare customised bookdown


```{r function-3}
#' Prepare customised bookdown from skeleton and template
#' This function creates an Rstudio project in path, sets build type to "website", copies the content of book_skeleton at the root of the project, copies all files from the book template, modifies pre-defined variable book_title, author_name, creation_date, as well as any variable added by the user in replacements (index_title, index_content...), and inserts the content of index.txt in index.Rmd (here containing the user defined variables index_title and index_content).   
#'
#' @param path where to create the bookdown
#' @param template path to directory containing template files for chapters and index content
#' @inheritParams find_and_replace
#' @inheritParams prepare_files
#' @importFrom usethis create_project
#'
#' @return
#' @export
#'
#' @examples
prepare_book <- function(
                         path,
                         replacements = c(
                           "book_title" = "My book",
                           "author_name" = "Marion Louveaux",
                           "creation_date" = "`r Sys.Date()`",
                           "short_description" = "An example of book with {bookprep}.",
                           "index_title" = "Context"
                         ),
                         template = system.file("book_template_example", package = "bookprep"),
                         pattern = "[.]Rmd$|[.]yml$|[.]md$") {
  # Create project
  path <- normalizePath(path)
  create_project(path = path, open = FALSE)
  # Modify buildType: "BuildType: Package" to "BuildType: Website"
  proj_lines <- readLines(list.files(path, pattern = "[.]Rproj$", full.names = TRUE))
  proj_lines_modified <- str_replace(string = proj_lines,
                                              pattern = "BuildType: Package",
                                              replacement = "BuildType: Website")
  writeLines(text = proj_lines_modified, con = list.files(path, pattern = "[.]Rproj$", full.names = TRUE))

  # Add all files from book skeleton
  skeleton_dir <- system.file("book_skeleton", package = "bookprep")
  file.copy(from = list.files(skeleton_dir, full.names = TRUE), to = path, recursive = TRUE)

  # Add all files from book template (Rmd, css...) except index     
  if (!dir.exists(template)){ # by default use the template of the package
    stop(template, ' directory does not exist.') # means that user provided a incorrect path to a custom template
  }
  all_files_wo_index <- list.files(normalizePath(template), full.names = TRUE)
  all_files_wo_index <- all_files_wo_index[!grepl("^index", basename(all_files_wo_index))]
  file.copy(from = all_files_wo_index, to = path, recursive = TRUE)

# Detect css files and modify _output.yml
extra_css <- basename(all_files_wo_index)[grepl("[.]css$", basename(all_files_wo_index))]
if (length(extra_css) != 0) {
  output_lines <- readLines(file.path(path, "_output.yml"))
  output_modified <- str_replace(
    string = output_lines,
    pattern = "css: style.css",
    replacement = paste0(
      "css: [style.css, ",
      paste(extra_css, collapse = ","), "]"
    )
  )
  writeLines(text = output_modified, con = file.path(path, "_output.yml"))
}

  # Copy content from index.md or index.txt
  # NB: this content can contain variables such as index_title and index_content       
  index_txt <- grep(
    pattern = "index[.](txt|md)$",
    list.files(template)
  )
  index_content_from_txt <- readLines(list.files(template, full.names = TRUE)[index_txt])
  index_rmd_path <- list.files(path, pattern = "^index[.]Rmd$", full.names = TRUE)

  # Concatenate and write current index.Rmd with content from index.md or index.txt    
  new_index_content <- c(
    readLines(index_rmd_path),
    index_content_from_txt
  )
  writeLines(enc2utf8(new_index_content), con = index_rmd_path)

  # Modify files for replacements
  prepare_files(
    path = path,
    replacements = replacements,
    pattern = pattern
  )
}
```


```{r examples-3}
# Create temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)
# browseURL(dir_tmp)

prepare_book(
  path = dir_tmp,
  template = system.file("book_template_example", package = "bookprep"),
  replacements = c(
    # replacements mandatory for the bookdown skeleton
    "book_title" = "My book",
    "author_name" = "Marion Louveaux",
    "creation_date" = "`r Sys.Date()`",
    "short_description" = "An example of book with {bookprep}.",
    # replacement specific to my template that you can add if you want
    "index_title" = "Context"
  )
)
```

```{r tests-3}
# Create temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)
# browseURL(dir_tmp)

usethis::with_project(
  getwd(),
  prepare_book(
    path = dir_tmp,
    template = system.file("book_template_example", package = "bookprep"),
    replacements = c(
      # replacements mandatory for the bookdown skeleton
      "book_title" = "My book",
      "author_name" = "Marion Louveaux",
      "creation_date" = "`r Sys.Date()`",
      "short_description" = "An example of book with {bookprep}.",
      # replacement specific to my template (variable in index.md)     
      "index_title" = "Context"
    )
  )
)

test_that("prepare_book works", {
  expect_true(file.exists(file.path(dir_tmp, "index.Rmd")))
  # checks that Rproj exists
  rproj_path <- list.files(dir_tmp, pattern = "[.]Rproj$", full.names = TRUE)
  expect_length(rproj_path, 1)
  # Checks that build type is website in Rproj
  rproj_content <- readLines(rproj_path)
  expect_equal(rproj_content[14], "BuildType: Website")
  # Checks that there is an extra.css file in the book template example
  css_path <- list.files(system.file("book_template_example", package = "bookprep"),
                         pattern = "extra[.]css$")
  expect_length(css_path, 1)
  # Checks that the extra.css is in the _output.yml 
  outputyml_path <- list.files(dir_tmp, pattern = "_output[.]yml$", full.names = TRUE) 
  outputyml_content <- readLines(outputyml_path)
  expect_length(grep(outputyml_content[2], pattern = "extra[.]css"), 1)
  # Checks that content of index.md has been copied in index.Rmd and index_title replaced 
  
  index_path <- list.files(dir_tmp, pattern = "index[.]Rmd$", full.names = TRUE) 
  index_content <- readLines(index_path)
  expect_equal(index_content[12], paste0("# ", "Context"))
  expect_equal(index_content[13], "")
  expect_equal(index_content[14], "Write here what you want to see in the <span class=\"red\">index</span>")
})
```


# Initialize a template

- index.txt or index.md: Level 1 title and/or content     
- Some Rmd files    


```{r function-4}
#' Initialize a book template with named chapters and content for 
#'
#' @param path
#' @param chapters
#' @param references
#'
#' @return
#' @export
#'
#' @examples
initialize_template <- function(path, chapters = c("Preface", "Introduction"),
                                references = "References") {
  rmd_tmp <- c(chapters, references)
  rmd_files <- sprintf("%02d-%s.Rmd", seq_along(rmd_tmp) -
    1, rmd_tmp)

  titles <- c(chapters, sprintf(
    "`r if (knitr::is_html_output()) '# %s {-}'`",
    references
  )) %>%
    paste("#", .)

  for (i in seq_along(rmd_files)) {
    file_tmp <- rmd_files[i]
    if (file.exists(file_tmp)) {
      stop("The file ", file_tmp, " exists.")
    } else {
      write_utf8(titles[i], file_tmp)
    }
  }

}
```

```{r examples-4}

```

```{r tests-4}

```



# Add a custom bib file

The book skeleton includes a book.bib file containing references to bookdown and bookprep. The function below copies a new .bib file to the root of the project and modifies the index.Rmd to add this file.      


```{r function-5}

```


```{r examples-5}

```

```{r tests-5}

```


