---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bookprep)
```

# Bookdown skeleton creation     

The function `prepare_book()` requires a {bookdown} skeleton and a template. The {bookdown} skeleton contains only the following files: "_bookdown.yml", "_output.yml", "index.Rmd", "preamble.tex", "README.md", and "style.css". These files condition the architecture (the skeleton) of the future book, i.e. how it will be printed/rendered, its css style, link to bibliography and information about author, title and creation date. By default, `prepare_book()` uses the skeleton stored in `/book_skeleton` in the {bookprep} package. You can use your own skeleton if you prefer.        

The {bookdown} skeleton created for the {bookprep} package was created by cleaning info specific to the {bookdown} package and replacing them by generic variable names:      
- Index.Rmd: create variable book_title, author_name, creation_date (default to `Sys.Date()`), short_description, index_title and index_content   
- _bookdown.yml: reuse book_title variable  
- _output.yml: reuse book_title variable, add info that this book was published with {bookprep}             
- README.md: reuse variable book_title and specifies that this book was published with {bookprep}             



# Template creation     

The template contains Rmd files corresponding to the named chapters, an index.md file containing the content of the future index and, if needed, an extra .css file and an extra .bib file. Named chapters and index.md can include variables. These variables can be replaced with custom content using the `replacements` parameter of `prepare_book()`.    

An example of template is included in {bookprep} in `/book_template_example`. You can also provide your own template, or create a minimal one using the function `initialize_template()`.    


<!-- 

# Find and replace all variables in one text file of the book skeleton

-->

<!-- 

```{r examples-1}
# copy to a temporary file to avoid overwriting the package
index_tmp <- tempfile(pattern = "index-")

file.copy(from = system.file("book_skeleton/index.Rmd", package = "bookprep"), to = index_tmp)

bookprep:::find_and_replace(
  file = index_tmp,
  replacements = c(
    "book_title" = "My book",
    "author_name" = "Marion Louveaux",
    "creation_date" = "`r Sys.Date()`",
    "short_description" = "An example of book with {bookprep}.",
    "index_title" = "Context"
  )
)
```

-->



<!-- 

# Modify all variables in all files

-->

<!-- 

```{r examples-2}
# Create temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)
# browseURL(dir_tmp)

# prepare_files() requires a directory with some files inside to look for replacements
file.copy(from = system.file("book_skeleton", package = "bookprep"), to = dir_tmp, recursive = TRUE)

bookprep:::prepare_files(
  path = dir_tmp,
  replacements = c(
    "book_title" = "My book",
    "author_name" = "Marion Louveaux",
    "creation_date" = "`r Sys.Date()`",
    "short_description" = "An example of book with {bookprep}.",
    "index_title" = "Context"
  )
)
```

-->



# Prepare customised bookdown

```{r examples-3, eval = FALSE}
# Create temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)
# browseURL(dir_tmp)

prepare_book(
  path = dir_tmp,
  template = system.file("book_template_example", package = "bookprep"),
  replacements = c(
    # replacements mandatory for the bookdown skeleton
    "book_title" = "My book",
    "author_name" = "Marion Louveaux",
    "creation_date" = "`r Sys.Date()`",
    "short_description" = "An example of book with {bookprep}.",
    # replacement specific to my template that you can add if you want
    "index_title" = "Context"
  )
)
```

# Initialize a template

- index.txt or index.md: Level 1 title and index content     
- some Rmd files    


```{r examples-4}
# Create temporary directory for reproducible example
dir_tmp <- tempfile(pattern = "proj-")
dir.create(dir_tmp)
# browseURL(dir_tmp)

initialize_template(path = dir_tmp, 
                    chapters = c("Introduction", "Material and Methods",
                                 "Results", "Discussion"),
                                references = NULL)
```

# Add a custom bib file

The book skeleton includes a book.bib file containing references to {bookdown} and {bookprep}. The function below copies a new .bib file to the root of the project and modifies the index.Rmd to add this file.      



```{r examples-5}

```

